\documentclass[14pt, a4paper, sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}

\pdfgentounicode=1

\usepackage[scale=0.88]{geometry}
\setlength{\hintscolumnwidth}{4cm}

\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\normalsize}{\fontsize{13}{16}\selectfont}
\renewcommand{\baselinestretch}{1.2}

\firstname{Soroush}
\familyname{Kazemi}

\title{Technology Leader}
\address{}{Sydney, NSW}
\newcommand{\phoneNumber}{PHONE_NUMBER_PLACEHOLDER}
\newcommand{\emailAddress}{EMAIL_ADDRESS_PLACEHOLDER}
\newcommand{\homePage}{HOMEPAGE_PLACEHOLDER}

\ifthenelse{\equal{\phoneNumber}{}}{}{\mobile{\phoneNumber}}
\ifthenelse{\equal{\emailAddress}{}}{}{\email{\emailAddress}}
\ifthenelse{\equal{\homePage}{}}{}{\homepage{\homePage}{}}
\renewcommand*{\quotefont}{\small\slshape}

\quote{
    \begin{minipage}{\quotewidth}
        \textit{
            \fontsize{13}{16}\selectfont
            A technology leader with extensive experience building scalable cloud platforms, fostering collaboration, and driving engineering solutions that align with business goals.
            I love delivering the product features customers want, improving business processes, and making internal users' lives easier --- practising strong engineering standards, pair programming, and agility.
        }
    \end{minipage}
}

\begin{document}

    \makecvtitle

    \section{Experience}\label{sec:experience}

    \cventry
    {Jan 2024 -- Present}
    {Senior Manager}
    {\newline \textcolor{gray}{Macquarie Group}}
    {\textcolor{gray}{Sydney}}
    {\textcolor{gray}{Australia}}
    {
        \fontsize{13}{16}\selectfont
        Leading the development of a company-wide cloud control plane. Driving engineering excellence through automation, CI/CD, and quality-driven practices.
        \begin{itemize}
            \item Led the design and delivery of a company-wide cloud control plane, enabling teams to self-serve AWS services through standardised, secure abstractions with built-in governance, controls, and guardrails.
            \item Owned and delivered a major cloud storage migration, replacing on-premises infrastructure and reducing costs by tens of thousands of dollars per month while improving scalability and resilience.
            \item Established engineering standards and automation across CI/CD, testing, and release pipelines, significantly improving delivery speed, reliability, and operational consistency.
            \item Mentored engineers and provided technical leadership across cloud architecture, platform design, and operational best practices, lifting overall team capability.
            \item Tech: .NET, Go, Python, AWS (EKS, FSx, Glue, Bedrock, Lambda, SQS, SNS), React, Crossplane, Argo, Terraform, GitHub, OTEL.
        \end{itemize}
    }

    \cventry
    {Mar 2020 -- Jan 2024}
    {Lead Software Engineer}
    {\newline \textcolor{gray}{Evergen}}
    {\textcolor{gray}{Sydney}}
    {\textcolor{gray}{Australia}}
    {
        \fontsize{13}{16}\selectfont
        Designed and built an energy asset orchestration platform, focusing on quality, reliability, and scalability. Led cross-functional teams to deliver cloud-native solutions and fostered a collaborative team culture.
        \begin{itemize}
            \item Built microservices in Golang, .NET Core, and React, deployed on AWS, Kubernetes, and Kafka.
            \item Implemented CI/CD pipelines and advanced instrumentation to streamline development and ensure platform reliability.
            \item Proposed and executed initiatives to improve onboarding, reducing time-to-productivity for new engineers by multiple factors.
            \item Mentored junior engineers, elevating team productivity and fostering a collaborative culture.
            \item Tech: Go, React, AWS (Lambda, ElastiCache, Athena, SageMaker), K8s, MongoDB, Bitbucket.
        \end{itemize}
    }

    \cventry
    {May 2019 -- Feb 2020}
    {Senior Software Engineer}
    {\newline \textcolor{gray}{DriveYello}}
    {\textcolor{gray}{Sydney}}
    {\textcolor{gray}{Australia}}
    {
        \fontsize{13}{16}\selectfont
        Contributed to the development of a last-mile delivery platform servicing B2B clients.
        \begin{itemize}
            \item Developed backend features using PHP frameworks and Node.js to manage order workflows, delivery tracking, and vendor integrations.
            \item Maintained and deployed services on AWS using Docker containers, orchestrated with Rancher in production.
            \item Collaborated with cross-functional teams to improve system stability and streamline delivery processes, despite infrastructure limitations.
            \item Tech: PHP, Go, Node.js, AWS (Lambda, EKS), OTEL, Bitbucket.
        \end{itemize}
    }

    \cventry
    {Oct 2018 -- Apr 2019}
    {Technical Team Lead}
    {\newline \textcolor{gray}{Netbina}}
    {\textcolor{gray}{Tehran}}
    {\textcolor{gray}{Iran}}
    {
        \fontsize{13}{16}\selectfont
        Led the development of sentiment analysis systems at a digital advertising agency, enabling data-driven brand promotion across social media platforms.
        \begin{itemize}
            \item Created a sentiment analysis pipeline using Laravel and MySQL, tailored for analysing social media content.
            \item Extracted insights from public conversations to support brand campaigns and digital marketing strategies.
            \item Delivered reliable, scalable backend solutions that empowered the marketing team to measure brand perception and improve targeting.
            \item Tech: PHP (Laravel), Go, Elasticsearch, K8s, Grafana, MySQL.
        \end{itemize}
    }

    \cventry
    {Apr 2018 -- Oct 2018}
    {Senior Software Engineer}
    {\newline \textcolor{gray}{Snappfood}}
    {\textcolor{gray}{Tehran}}
    {\textcolor{gray}{Iran}}
    {
        \fontsize{13}{16}\selectfont
        Built a high-performance, index-based search engine for fast searches across restaurants, food items, and grocery products. Designed and implemented a scalable solution on Elasticsearch capable of handling millions of entries, deployed on-prem with Kubernetes and Docker.
    }

    \cventry
    {Sep 2009 -- Apr 2018}
    {Software Engineer}
    {\newline \textcolor{gray}{Saba System Sadra}}
    {\textcolor{gray}{Tehran}}
    {\textcolor{gray}{Iran}}
    {
        \fontsize{13}{16}\selectfont
        Built a Security Information and Event Management (SIEM) platform that helps organisations detect and respond to cyber threats. Application in PHP and Laravel; SIEM engine on Elasticsearch, Logstash, and Kibana.
    }


    \section{Education}\label{sec:education}

    \cventry
    {2014 -- 2016}
    {Master of Science (M.Sc.)}
    {Amirkabir University of Technology}
    {Tehran}
    {Iran}
    {Computer Systems Networking and Telecommunications}

    \cventry{2009 -- 2014}
    {Bachelor of Science (B.Sc.)}
    {Amirkabir University of Technology}
    {Tehran}
    {Iran}
    {Information Technology}


    \section{Skills}\label{sec:skills}

    \cvitem{Cloud \& Platform}{AWS (EKS, Lambda, Athena, Glue, Bedrock, FSx, SNS, SQS, MSK, OpenSearch), Kubernetes, Terraform, AWS CDK}
    \cvitem{Automation \& CI/CD}{GitHub, Bitbucket, Argo, OpenTelemetry}
    \cvitem{Programming}{Go, Python, .NET, Node.js, React}

    \section{References}\label{sec:references}
    \cvitem{}{Available on request}

\end{document}
